Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2022-11-17 latex/comp_or.tex
Shared data in parallel processing

@@

The decision for {\it Multiprocessing} relies on the need to exchange information among processes (the pheromone trails or some information regarding load balancing, in our case), which would be harder to handle with thread-based parallelism. For this, we used the multiprocessing queue feature that, according to \cite{multiprocessing}, is thread safe.

@@

Observing Figure \ref{fig:scenario1data20}, it may be noticed that the best number of processes for {\it Scenario 1} (the closest to the {\it Utopia}) is \textbf{6}. For {\it Scenario 2}, the best number is \textbf{4}.

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf mpShims computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/Shims_p1data50.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf mpACO computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/ACO_p1data50.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}

	\end{center}
	\caption{ Scenario 1 performances with $1.5 \times volume$. }
	\label{fig:scenario1data50}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf mpShims computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/Shims_p2data20.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf mpACO computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/ACO_p2data20.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}

	\end{center}
	\caption{ Scenario 2 performances with $1.2 \times volume$. }
	\label{fig:scenario2data20}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf mpShims computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/Shims_p2data50.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf mpACO computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {./csv/ACO_p2data50.csv};
			\end{axis}
			\fill [red] (canvas cs:x=0.1cm,y=5.6cm) circle (2pt);
		\end{tikzpicture}

	\end{center}
	\caption{ Scenario 2 performances with $1.5 \times volume$. }
	\label{fig:scenario2data50}
\end{figure}

%Observing figures \ref{fig:mpShimsdata20}, \ref{fig:mpShimsdata50}, \ref{fig:mpACOdata20}, \ref{fig:mpACOdata50}, it may be noticed that the best overall number of processes for all scenarios is \textbf{?}, because in average it is the number that most of the times is closer to the {\it Utopia} red bullet.

@@

\begin{table}[H]
	\centering
	\caption{Methods and scenarios with $1.2 \times volume$}  \label{tab:20}
%	\footnotesize
\scriptsize
	\begin{tabular}{r|c|c|cccccc|c}
		\toprule
		{$method$}                     &{\bf Procs}              &{\bf Results}     &{\bf 1}     &{\bf 2}    &{\bf 3}      &{\bf 4}      &{\bf 5}      &{\bf 6}     &\specialcell{{\bf Normalized}\\{\bf Speed-up}} \\
		\toprule

		\multirow{2}{*}{\it {Shims}}   &\multirow{2}{*}{\bf {1}} & $f$              & 5.40        & 2.94    & 2.93         &          &          &         &   \\ 
		                               &                         &{\bf run-time (s)}& <1          & 1       & 4            &            &            &          &   \\ %206s
		\midrule[.1pt]

		\multirow{2}{*}{\it {mpShims}} &\multirow{2}{*}{\bf {?}}& $f$              & 5.88        & 3.16    & 3.16         &          &          &         &   \\ 
		                               &                         &{\bf run-time (s)}& 1           & 10      & 41           &            &            &          &   \\ %299s
		\midrule[.1pt]

		\multirow{2}{*}{\it {ACO}}     &\multirow{2}{*}{\bf {1}} & $f$              & 5.77        & 3.49    & 3.02         &        &       &      &   \\ 
                                       &                         &{\bf run-time (s)}& 14          & 808     & 2398          &        &       &      &   \\ 
        \midrule[.1pt]

        \multirow{2}{*}{\it {mpACO}}   &\multirow{2}{*}{\bf {?}}& $f$              & 5.82        & 3.12    &          &         &       &       &   \\ 
                                       &                         &{\bf run-time (s)}& 22          & 473     &           &         &       &       &   \\

        \bottomrule		
	\end{tabular}

@@

\section{Conclusions}
\label{sec7}

>>>>

According to \cite[p.226]{manfrin2006}, there are five topologies for multi-process interchange of information: {\it fully-connected}, where the master process broadcasts to all remaining child processes; {\it replace-worst}, where the best-so-far solution process broadcasts only to the current worst solution process; {\it hypercube}, where processes are connected as a hypercube, and a vertex process broadcasts only to the connected vertices; {\it ring}, in which one process only sends a message to the next process connected to it; and {\it parallel independent runs (PIR)}, in which there are no communication costs and the best solution is chosen among all processes. They concluded that the PIR topology presented, in average, the smallest distance from the optimal solutions.

@@

@@

Observing Figure \ref{fig:scenario1data20}, it may be noticed that the best number of processes for {\it Scenario 1} (the closest to the {\it Utopia}) is \textbf{6}. For {\it Scenario 2}, the best number is \textbf{4}. Table \ref{tab:numProcs} presents all methods, volumes percentages and scenarios numbers of best parallel processes to be run to solve all tours.

To build Table \ref{tab:numProcs}, it was necessary to determine the number of parallel processes that best solve each node. For this we created a procedure as in Algorithm \ref{alg:bestnum}.

\begin{algorithm}[H]
	\caption{$getBestNPP(procs, scores, runtimes)$}  \label{alg:bestnum}
	\begin{algorithmic}[1]
		\State $maxS   \gets max(scores)$
		\State $minS   \gets min(scores)$
		\State $maxR \gets max(runtimes)$
		\State $minR \gets min(runtimes)$

		\State $bestNPP \gets 0$, best number of parallel processes
		\State $minD \gets 999999999.9$

		\For{$i$ in $procs$}
			\State $y = ( maxS - scores[i] )\ /\ (maxS   - minS  )$
			\State $x = ( runtimes[i] - minR )\ /\ (maxR - minR)$
			\State $h = \sqrt{x^2 + y^2}$, distance from {\it Utopia}
			\If{$minD$ > $h$}
				\State $minD \gets h$
				\State $bestNPP \gets procs[i]$
			\EndIf

		\EndFor

		\State ${\bf return}$ $bestNPP$
	\end{algorithmic}
\end{algorithm}

@@

\begin{table}[H]
\centering
\caption{$bestNPP$ found for each scenario}  \label{tab:numProcs}
	\footnotesize
%\scriptsize
\begin{tabular}{rccccccc}
\toprule
                               &               &\multicolumn{6}{c}{\bf Scenarios} \\
                               \cmidrule{3-8}
{$method$}                     &{\it volume}&{\bf 1}&{\bf 2}&{\bf 3}&{\bf 4}&{\bf 5}&{\bf 6} \\
\toprule

\multirow{3}{*}{\it {mpShims}} &$1.2$& 6       & 2     & 0     & 0     & 0     & 0    \\ 
                               &$1.5$& 4       & 4     & 0     & 0     & 0     & 0    \\
                               &$2.0$& 0       & 0     & 0     & 0     & 0     & 0    \\
\midrule[.1pt]

\multirow{3}{*}{\it {mpACO}}   &$1.2$& 4       & 2     & 0     & 0     & 0     & 0    \\ 
                               &$1.5$& 6       & 1     & 0     & 0     & 0     & 0    \\ 
                               &$2.0$& 0       & 0     & 0     & 0     & 0     & 0    \\                               
\bottomrule		
\end{tabular}

@@

Table \ref{tab:numProcs} presents the best numbers of parallel processes for each method, scenario, and volume surplus.

\begin{table}[H]
\centering
\caption{Methods and scenarios with $1.2 \times volume$}  \label{tab:20}
\footnotesize
%\scriptsize
\begin{tabular}{rccccccc|c}
\toprule
                                &                &\multicolumn{6}{c}{\bf Scenarios} &\\
\cmidrule{3-8}		
{$method$}                      &{\bf Results}   &{\bf 1}&{\bf 2}&{\bf 3}&{\bf 4}&{\bf 5}&{\bf 6}&\specialcell{{\bf Normalized}\\{\bf Speed-up}} \\
\toprule
\multirow{2}{*}{\it {mpShims}} & $f$              & 5.88 & 3.16    & 3.16 &      &      &      &   \\ 
                               &{\bf run-time (s)}& 1    & 10      & 41   &      &      &      &   \\
\midrule

\multirow{2}{*}{\it {mpACO}}   & $f$              & 5.82 & 3.12    &      &      &      &      &   \\ 
                               &{\bf run-time (s)}& 22   & 473     &      &      &      &      &   \\ 
\bottomrule		
\end{tabular}

\section{Conclusions}
